---
title: "Shopify Data Challenge"
author: "Richard Chen"
date: "9/11/2021"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE}
library(dplyr)
```

```{r load_data}
# download dataset from Google Sheets, rename to `shopify.csv`
shopify <- read.csv("~/Downloads/shopify.csv")
```

```{r naive_calculation}
# naive AOV check
mean(shopify$order_amount)
```

## Question 1

### Part a

Although the naive calculation of AOV is not necessarily incorrect, it is a sub-optimal evaluation of the data. 
The naive approach would be appropriate if both the total items and order amounts of all the orders were within
a certain order of magnitude, but that is not the case. Although most orders (~97%) have less than 10 items and 
most shoes are priced under $200.00, outliers with orders sizes of 2000 items and shoes priced at \$25,725.00 
drastically impact the naive calculation of AOV. Despite these outliers making up roughly 3% of all orders, 
their extremity is so many magnitudes larger than the other 97% of orders that a naive calculation of AOV is 
severely affected.

I explored various approaches to better evaluate the data and report an AOV more reflective of the overall dataset.
My methods included removing orders that exceeded a threshold for `order_amount` that I set at $10,000.00, 
removing orders that exceeded a threshold for `total_items` set at 10, examining the median order value instead, 
and calculating a mean item value of each shoe as opposed to each order.

I set the thresholds for `order_amount` and `total_items` to $10,000.00 and 10 respectively as a result of a
quick overview of the data. The largest percent increase in `order_amount` was from \$1760.00 to \$25,725.00, 
and from 8 to 2000 for `total_itmes`, so I felt that these thresholds were appropriate given the extreme 
difference in magnitude for these orders. 


```{r alternative_methods, results=FALSE}
# remove orders with high totals (arbitrary))
shopify %>% 
  filter(order_amount < 10000) %>%
  summarise(mean(order_amount))

# remove orders with high number of items (arbitrary)
shopify %>% 
  filter(total_items < 10) %>%
  summarise(mean(order_amount))

# look at median order value instead of mean
shopify %>% 
  summarise(median(order_amount))

# look at mean 'item' value of all shoes sold
sum(shopify$order_amount) / sum(shopify$total_items)

# check shoe price is same for all orders of every shop, 
#   ensuring `order_amount` is not an error in reporting
#   for orders with extremely high amount totals
shop_shoe_price <- shopify %>% 
  mutate(shoe_price = order_amount / total_items) %>%
  select(shoe_price, shop_id) %>%
  distinct()
```

Through another check, and using a more grounded method in detecting outliers via IQR rather than 
eyeballing it as above, I calculated the AOV as \$293.71, not too far off from the AOV of \$302.58 above.

```{r iqr, results=FALSE} 
# check AOV after removing IQR outliers
quantiles <- quantile(shopify$order_amount, probs = c(.25, .75), na.rm = FALSE)
iqr <- IQR(shopify$order_amount)
up <-  quantiles[2] + 1.5*iqr
low <- quantiles[1] - 1.5*iqr 
shopify <- shopify %>%
  mutate(iqr_outlier = case_when(order_amount > up ~ 1,
                                 order_amount < up ~ 0))

shopify %>%
  filter(iqr_outlier == 0) %>%
  summarise(mean(order_amount))
```

### Part b

I ultimately decided to calculate a AOV that did not include the two shops with `shop_id` 42 and 78. 
Shop 78 appears to sell a form of high-end luxury shoe priced at $25,725.00 per shoe. Shop 42 appears 
to sell shoes in bulk orders of 2000 items, and their shoes are also the second most expensive priced 
at \$352.00. As these two shops are drastically different from the other 98 shops in terms of the 
market they are targeting (extremely high-end clients and mass distributors or retail centers), 
I decided to remove them and their orders from the AOV calculation. 

### Part c 
As a result, I calculated the AOV as \$300.16, much more reasonable than the initial naive 
calculation of \$3145.13.

```{r alternative_methods2}
# calculate AOV without shops 42 and 78
shopify %>% 
  filter(shop_id != 42 & shop_id != 78) %>%
  summarise(mean(order_amount))
```


## Question 2

Please see attached file for SQL queries.


### Part a

Speedy Express shipped a total of 54 orders.

### Part b

Peacock had the most orders with 40.

### Part c

Boston Crab Meat was the most ordered product by customers in Germany with a total quantity of 160 units.
